Predictions

### 2021-04-07 analysis/04_predictions.Rmd
PHEWWWW ALL READY FOR ISA
Fix trimming issues with 2014 + use relative paths for data

```{r kludgy-bandaid-for-weird-data-issues}
# OOOOOOOF OH NO for some reason PTS_lead1 and all leaded V-Dem values missing
# for 2013 (i.e. 2014 values) and I don't want to go back and rerun all these
# models yet, so we do a temporary fix here and manually add the values from
# pts_clean and vdem_clean
withr::with_dir(here::here(), {
  tar_load(pts_clean)
  tar_load(vdem_clean)
})

pts_2014 <- pts_clean %>% 
  group_by(gwcode) %>% 
  mutate(across(c(PTS, PTS_factor),
                  list(lead1_2014 = ~lead(., 1)))) %>% 
  ungroup() %>% 
  filter(year == 2013) %>% 
  select(-PTS, -PTS_factor)

vdem_2014 <- vdem_clean %>% 
  group_by(gwcode) %>% 
  mutate(across(c(v2x_clphy, v2x_clpriv),
                  list(lead1_2014 = ~lead(., 1)))) %>% 
  ungroup() %>% 
  filter(year == 2013) %>% 
  select(gwcode, year, v2x_clphy_lead1_2014, v2x_clpriv_lead1_2014)

canary_testing_lagged <- canary_testing_lagged %>% 
  left_join(pts_2014, by = c("year", "gwcode")) %>% 
  left_join(vdem_2014, by = c("year", "gwcode")) %>% 
  mutate(PTS_lead1 = coalesce(PTS_lead1, PTS_lead1_2014),
         PTS_factor_lead1 = coalesce(PTS_factor_lead1, PTS_factor_lead1_2014),
         v2x_clphy_lead1 = coalesce(v2x_clphy_lead1, v2x_clphy_lead1_2014),
         v2x_clpriv_lead1 = coalesce(v2x_clpriv_lead1, v2x_clpriv_lead1_2014)) %>% 
  select(-contains("_2014"))
```

@@

pts_pred_table %>% 
  kbl(align = "lcccc") %>% 
  kable_styling()
```

>>>>

@@

pts_pred_table %>% 
  kbl(align = "lccccc") %>% 
  kable_styling()
```
